The first high-redshift Changing Look Quasars

### 2019-11-14 tex/CIV_CLQs.tex
ALLWISE_catalog.dat data added x3

The optical continuum variability of quasars has been recognized since
their first optical identification
\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic changes
in the broad emission lines (BELs) of quasars has only recently been
identified \citep[e.g., ][]{LaMassa2015}.  Samples of over 100
``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs)
have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019b}. The
community uses both these terms as a cover for the underlying
physics. For sake of argument, CLQs can potentially be thought of as
the extension to the BELs of quasar continuum variability \citep[e.g.,
][]{MacLeod2012} whereas the CSQs have a `state-transition' similar to
that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019}. In
this paper, we use the term `Changing Look', as we are currently
agnostic, and confessedly ignorant, to the underlying physical
processes.

>>>>

The optical continuum variability of quasars has been recognized since
their first optical identification
\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic changes
in the broad emission lines (BELs) of quasars has only recently been
identified \citep[e.g., ][]{LaMassa2015}.  Samples of over 100
``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs)
have now been assembled \citep[e.g.][]{MacLeod2019, Graham2019b}. The
community uses both these terms as a cover for the underlying
physics. For sake of argument, CLQs can potentially be thought of as
the extension to the BELs of quasar continuum variability \citep[e.g.,
][]{MacLeod2012} whereas the CSQs have a `state-transition' similar to
that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019}. In
this paper, we use the term `Changing Look', as we are currently
agnostic, and confessedly ignorant, to the underlying physical
processes.
